Technical Report

### 2017-11-08 fully-abstract-comp/technical-report.tex
Added a new argument to call, namely the offset in the seal that it uses.

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\scca}[2]{\twoinstr{\src{cca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\src{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}
% scall - special two instruction
\newcommand{\scall}[3][]{  
\ifthenelse{\equal{#2#3}{}}
  {\ensuremath{\zinstr{\src{call}}_{#1}}}
  {\ensuremath{\zinstr{\src{call}}_{#1} \; #2 \; #3}}
}

@@

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine is going to have a built in stack along with special stack and return capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    \src{r} &\in &  \RegName\\
    \src{\rn} &\defbnf & \src{r} \mid n \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{\src{r}}{\src{r}}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{}{}$ instruction.

The source machine allows for variable length instructions which we utilize for $\scall{}{}$. In other words, when we $\scall{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction. This is described in more detail when we present the decoding function.

@@

\paragraph{Step relation}
The instruction $\scall{}{}$ has length $\calllen$ which means that it does not fit on one memory address. In fact, $\scall{}{}$ should be seen as a different way of interpreting a series of instruction rather than an instruction on its own. We therefore introduce $\scall[1]{r_1}{r_2},\dots,\scall[\calllen-1]{r_1}{r_2}$ as aliases for the instructions that constitute $\scall{r_1}{r_2}$ (see Paragraph~\ref{par:call-impl} for details). We define the following condition that indicates that $\aaddr$ is the first address of a $\scall{r_1}{r_2}$ instruction in the configuration $\Phi$:
\[
  \sourcecolor\left.
    \callCond{\Phi,r_1,r_2,\aaddr} = \left\{
      \begin{array}{l}
        \Phi.\mem(\aaddr) = \scall[1]{r_1}{r_2} \tand\\
        \vdots \\
        \Phi.\mem(\addr+\calllen-1) = \scall[\calllen]{r_1}{r_2}
      \end{array}
      \right.
  \right.
\]

@@

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \baddr \leq \aaddr \leq \eaddr\tand\\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{}{}$ implementation, i.e., the instructions $\scall[1]{r_1}{r_2} \dots \scall[\calllen]{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \text{// push 42 on the stack (so it is non-empty).}\\
    \tstore{\rstk}{42}\\
    \tcca{\rstk}{-1}\\
    \text{// split the stack at its current address - rstk done.}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \text{// load the seal for the return pointer through the pc capability.}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{{\color{red} \dots}}\\
    \text{// seal the used stack frame as the data part of the return pointer pair.}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    \text{// obtain the code part of the return pointer pair and seal it too.}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    \text{// now clear temporary register and jump to the adversary.}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \text{// check that the stack pointer is the same we handed out.}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \text{// join our stored private stack frame with the rest of the stack (this also finishes the stack pointer check).}\\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \text{// pop the magic number 42}\\
    \tcca{\rstk}{1}\\
    \text{// clear temporary registers used}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}\\
    \text{// continue program after invocation.}
  \end{array}
\]
\dominique{Return code could be simplified if we had jz in addition to jnz.}
\dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
  I understand this is for ensuring that our private stack frame is not empty, which is important.
  But why don't we just push a constant then?
  Also: perhaps we could only do it if the current private stack frame is empty to begin with?
}
{\color{red} \dots} needs to be the offset to the seal we want to use.
The call code does the following:
\begin{itemize}
\item Store the end address of the stack to the stack (this ensures the stack is non-empty), and decrement the pointer according to convention.
\item Get the current address of the stack pointer and split according to it.
\item Retrieve the seal of the program.
\item cca the seal, so the seal to be used is active 
\item seal our private part of the stack capability.
\item Move the pc out of the pc register, adjust it to point to the first address of the return code, and seal it.
\item clear the temporary register.
\item cross jump to the two specified registers.
\item Upon return:
  \begin{itemize}
  \item get the base of the stack and check that it matches up with the global base of the stack.If not, fail.
  \item splice the returned stack pointer and the stack pointer for our private stack.
  \item adjust stack pointer to first empty address (the address with the end address is considered free)  
  \item clear the temporary registers.
  \end{itemize}
\end{itemize}

@@

  \sem{\scall{\src{r_1}}{\src{r_2}}}(\Phi) = & 

@@

\[
  \comp{\scall{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

We want to make a conditional full-abstraction statement. The condition should express two things (1) the compilation so far has been reasonable, so we do not have to setup protection against things any reasonable compiler wouldn't do. (2) the compilation so far has taken care of certain checks that we do not have information to place correctly at this point of the compilation
\begin{definition}
  \label{def:check-stack-addr-before-call}
  A configuration $\src{\Phi}$ is said to have reasonable calls in $A$ for $n$ steps iff\\
  for all $i \leq n$ if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\scall{r_1}{r_2}}$ in $A$ for some $\src{r_1}$ and $\src{r_2'}$ and there exists no $j<i$ s.t.
  \[
    \src{\Phi} \nstep[j] \src{\Phi''}
  \]
  where $\src{\Phi''}$ points to $\src{\scall{r_1'}{r_2'}}$ in $A$ for some $\src{r_1'}$ and $\src{r_2'}$,
  then
  \[
    \src{\Phi}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\_,\_}}
  \]
  and $\src{\Phi'}$ has reasonable calls in $A$ for $n-i$ step.
\end{definition}

@@

\dominique{27-09-2017: Is this example still relevant? Isn't it solved differently by the variable-length-instructions idea?}
\lau{28-09-2017: It seems to me that this is indeed solved by the variable length instructions. That said, I would like to keep it around (maybe change it so it becomes an argument for variable length instructions).}
This example was introduced when we envisioned a capability machine with $\spush{}$, $\spop{}$, $\ssload{}{}$, $\scall{}{}$ and $\sreturn$ instructions. The below example is a motivation for having variable length instructions in the source language because if we have enough memory to ``do the same'' in the target language as in the source language, then the below example does not work.

@@

The context with $r1$ as an executable capability pointing to:
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
$\scall{r5}{0}$
$\sjmp{r5}$
\end{lstlisting}
\footnote{At this time $\scall{}{}$ did argument spilling and it only takes one argument because we were considering enter capabilities.}distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.

@@

We do not offer primitive \sreturn{}, \spush{} and \spop{} instructions, even though there is nothing keeping us from doing that, either as an additional primitive instruction or as a macro on top of the primitive token values mentioned above.
We do offer a primitive \scall{}{} instruction, and it offers the only way to create a new stack frame.
It is the only instruction that does not have a target language counterpart.
However, there is a counterpart to \sxjmp{}{}, the instruction that would be used for jumping in the code that \scall{}{} compiles to.
We will discuss later that this means that if we back translate an adversary piece of code (in the full abstraction proof), then it will be back translated (under our trivial back-translation) to equivalent code that \emph{never} does an actual call, but always just jumps to where it wants to go.
In other words, the back-translated code never uses call to protect its own stack frame from the code that it passes control to.
This means that the back-translated code is quite insecure, but we don't need it to be: it just needs to be behaviorally equivalent to the target language code that it represents.

% Finally, rather than invoking call, \dominique{7-9-2017: err, what's the reason we don't follow the same pattern for call?}.
% \lau{07-09-2017: One would use $\scall{}{}$ with a pair of sealed capabilities to securely jump to this pair - that is to have this pair executed in a new stack frame. The return would happen just by using $\sxjmp{}{}$ with the $\retptrd$ and $\retptrc$. However, this would work with the local capabilities as the real implementation of $\retptrd$ would be a sealed version of the entire stack pointer. In other words, upon jumping back no extra work would have to be done. Now, however, the old stack pointer should be spliced (using the new $\ssplice{}{}$ instruction) with the stack pointer we sent away in order to regain the old stack pointer. In other words, we need something to recognise when a return happens.}
% \lau{07-09-2017: On second thought, when compiled all the code necessary for the call will be generated based on the $\scall{}{}$ instruction. The real implementation of the $\retptrc$ will simply point to a piece of clean up code that splices together the old/private stack pointer with the one we got from the untrusted party. This may, however, give some issues when we want to reason about it because there will be a disconnect between where the clean up job is done in the operational semantics of the source language (namely as part of the $\sxjmp{}{}$), but in a translated program, the code that does the clean up origins with the $\scall{}{}$ instruction. }

@@

Another novelty in this work is the fact that we do not want to prove general full abstraction (i.e. two source programs are behaviorally equivalent if and only if they are compiled to behaviorally equivalent target programs).
The reason is that we only want to prove a result about programs that respect the calling convention, i.e.\ that do not do anything stupid.
For example, in the old setup with global/local capabilities, when trusted code performs an \scall{}{}, it should make sure that it does not store a copy of its stack pointer in a place that is accessible to the callee (e.g.\ in a register or in the callee's part of the stack).
Such sanity conditions are necessary (we cannot guarantee anything for code that does such stupid things) but we do not want to spend computation time on checking them.
Instead, we expect a reasonable compiler to guarantee in some way that its generated code never does such stupid things and then our guarantees should apply.

>>>>

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\scca}[2]{\twoinstr{\src{cca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\src{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}
% scall - special two instruction
\newcommand{\scall}[4][]{  
\ifthenelse{\equal{#3#4}{}}
  {\ensuremath{\zinstr{\src{call}}_{#1}^{#2}}}
  {\ensuremath{\zinstr{\src{call}}_{#1}^{#2} \; #3 \; #4}}
}

@@

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine is going to have a built in stack along with special stack and return capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    n & \in & \nats \\
    o & \in & \nats \\
    \src{r} &\in &  \RegName\\
    \src{\rn} &\defbnf & \src{r} \mid n \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{o}{\src{r}}{\src{r}}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{o}{}{}$ instruction (the $o$ refers to the seal it uses, namely the offset in the seals made available by linking).

The source machine allows for variable length instructions which we utilize for $\scall{o}{}{}$. In other words, when we $\scall{o}{}{}$ is decoded, a series of addresses in memory must contain what corresponds to the call instruction. This is described in more detail when we present the decoding function.

@@

\paragraph{Step relation}
The instruction $\scall{o}{}{}$ has length $\calllen$ which means that it does not fit on one memory address. In fact, $\scall{o}{}{}$ should be seen as a different way of interpreting a series of instruction rather than an instruction on its own. We therefore introduce $\scall[1]{o}{r_1}{r_2},\dots,\scall[\calllen-1]{o}{r_1}{r_2}$ as aliases for the instructions that constitute $\scall{o}{r_1}{r_2}$ (see Paragraph~\ref{par:call-impl} for details). We define the following condition that indicates that $\aaddr$ is the first address of a $\scall{o}{r_1}{r_2}$ instruction in the configuration $\Phi$:
\[
  \sourcecolor\left.
    \callCond{\Phi,r_1,r_2,\aaddr} = \left\{
      \begin{array}{l}
        \Phi.\mem(\aaddr) = \scall[1]{o}{r_1}{r_2} \tand\\
        \vdots \\
        \Phi.\mem(\addr+\calllen-1) = \scall[\calllen]{o}{r_1}{r_2}
      \end{array}
      \right.
  \right.
\]

@@

\begin{align*}
  \src{\Phi} & \; \src{\step \sem{\scall{o}{r_1}{r_2}}(\Phi)} &  &\sourcecolor\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \callCond{\Phi,r_1,r_2,\aaddr} \tand\\
                                                    \baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr \tand \\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi & \step \sem{\decInstr{\Phi.\mem(\aaddr)}}(\Phi) & &\left.\arraycolsep=0pt
                                                  \begin{array}[t]{l}
                                                    \text{if }\Phi(\pcreg) = ((\perm,\_),\baddr,\eaddr,\aaddr) \tand \\
                                                    \src{(\neg\callCond{\Phi,r_1,r_2,\aaddr} \tor}\\
                                                    \src{\eaddr < \aaddr + \calllen-1) \tand} \\
                                                    \baddr \leq \aaddr \leq \eaddr\tand\\
                                                    \exec{\Phi(\pcreg)}
                                                  \end{array}\right.\\
  \Phi& \step \failed & & \totherwise
\end{align*}

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{o}{}{}$ implementation, i.e., the instructions $\scall[1]{o}{r_1}{r_2} \dots \scall[\calllen]{o}{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{o}{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{o}{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \text{// push 42 on the stack (so it is non-empty).}\\
    \tstore{\rstk}{42}\\
    \tcca{\rstk}{-1}\\
    \text{// split the stack at its current address - rstk done.}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \text{// load the seal for the return pointer through the pc capability.}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{o}\text{ // $o$ is the offset this call uses.}\\
    \text{// seal the used stack frame as the data part of the return pointer pair.}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    \text{// obtain the code part of the return pointer pair and seal it too.}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    \text{// now clear temporary register and jump to the adversary.}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \text{// check that the stack pointer is the same we handed out.}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \text{// join our stored private stack frame with the rest of the stack (this also finishes the stack pointer check).}\\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \text{// pop the magic number 42}\\
    \tcca{\rstk}{1}\\
    \text{// clear temporary registers used}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}\\
    \text{// continue program after invocation.}
  \end{array}
\]
\dominique{Return code could be simplified if we had jz in addition to jnz.}
\dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
  I understand this is for ensuring that our private stack frame is not empty, which is important.
  But why don't we just push a constant then?
  Also: perhaps we could only do it if the current private stack frame is empty to begin with?
}
The call code does the following:
\begin{itemize}
\item Store the end address of the stack to the stack (this ensures the stack is non-empty), and decrement the pointer according to convention.
\item Get the current address of the stack pointer and split according to it.
\item Retrieve the seal of the program.
\item cca the seal, so the seal to be used is active 
\item seal our private part of the stack capability.
\item Move the pc out of the pc register, adjust it to point to the first address of the return code, and seal it.
\item clear the temporary register.
\item cross jump to the two specified registers.
\item Upon return:
  \begin{itemize}
  \item get the base of the stack and check that it matches up with the global base of the stack.If not, fail.
  \item splice the returned stack pointer and the stack pointer for our private stack.
  \item adjust stack pointer to first empty address (the address with the end address is considered free)  
  \item clear the temporary registers.
  \end{itemize}
\end{itemize}

@@

  \sem{\scall{o}{\src{r_1}}{\src{r_2}}}(\Phi) = & 

@@

\[
  \comp{\scall{o}{r_1}{r_2}} = 
  \begin{array}[t]{l}
    % Make the stack capability into the return capability and seal it:
    %   Push r_data to the stack (should this be made the responsibility of the programmer? If it happens here, then it should probably also be part of the call semantics. Especially, the call semantics should "eat" another piece of memory on the stack to make sure there is no discrepancy.)
    %   Seal the stack capability (with what? where does the seal come from? I think we talked about this, and it is something that should be handled like linking (a fresh seal is available in the beginning of a programs code along with a capability for a linking table)).
    % restrict the stack capability to the unused part (and clear this part (is this really necessary?)).
    % make return capability and ceal it:
    %   Move a copy of pc to a different register.
    %   Adjust the pc copy to point to the return address.
    %   Seal it with the seal.
    % remove all data from temp registers (that is at least the seal).
    % jmpx to r1 and r2
    % restore code:
    %   check the stack end address.
    %   move the stack pointer to the proper register
    %   pop the data capability
  \end{array}
\]

@@

We want to make a conditional full-abstraction statement. The condition should express two things (1) the compilation so far has been reasonable, so we do not have to setup protection against things any reasonable compiler wouldn't do. (2) the compilation so far has taken care of certain checks that we do not have information to place correctly at this point of the compilation
\begin{definition}
  \label{def:check-stack-addr-before-call}
  A configuration $\src{\Phi}$ is said to have reasonable calls in $A$ for $n$ steps iff\\
  for all $i \leq n$ if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'}
  \]
  and $\src{\Phi'}$ points to $\src{\scall{o}{r_1}{r_2}}$ in $A$ for some $\src{r_1}$ and $\src{r_2'}$ and there exists no $j<i$ s.t.
  \[
    \src{\Phi} \nstep[j] \src{\Phi''}
  \]
  where $\src{\Phi''}$ points to $\src{\scall{o}{r_1'}{r_2'}}$ in $A$ for some $\src{r_1'}$ and $\src{r_2'}$,
  then
  \[
    \src{\Phi}(\src{r_\stk}) = \src{\stkptr{\_,\stkb,\_,\_}}
  \]
  and $\src{\Phi'}$ has reasonable calls in $A$ for $n-i$ step.
\end{definition}

@@

\dominique{27-09-2017: Is this example still relevant? Isn't it solved differently by the variable-length-instructions idea?}
\lau{28-09-2017: It seems to me that this is indeed solved by the variable length instructions. That said, I would like to keep it around (maybe change it so it becomes an argument for variable length instructions).}
This example was introduced when we envisioned a capability machine with $\spush{}$, $\spop{}$, $\ssload{}{}$, $\scall{o}{}{}$ and $\sreturn$ instructions. The below example is a motivation for having variable length instructions in the source language because if we have enough memory to ``do the same'' in the target language as in the source language, then the below example does not work.

@@

The context with $r1$ as an executable capability pointing to:
\begin{lstlisting}[basicstyle=\sourcecolor{}\ttfamily] 
$\scall{o}{r5}{0}$
$\sjmp{r5}$
\end{lstlisting}
\footnote{At this time $\scall{o}{}{}$ did argument spilling and it only takes one argument because we were considering enter capabilities.}distinguishes the two contexts, but two instructions are not enough to do the same at the target level. We would not have enough instructions to set up a proper return pointer for the compiled return to use.

@@

We do not offer primitive \sreturn{}, \spush{} and \spop{} instructions, even though there is nothing keeping us from doing that, either as an additional primitive instruction or as a macro on top of the primitive token values mentioned above.
We do offer a primitive \scall{o}{}{} instruction, and it offers the only way to create a new stack frame.
It is the only instruction that does not have a target language counterpart.
However, there is a counterpart to \sxjmp{}{}, the instruction that would be used for jumping in the code that \scall{o}{}{} compiles to.
We will discuss later that this means that if we back translate an adversary piece of code (in the full abstraction proof), then it will be back translated (under our trivial back-translation) to equivalent code that \emph{never} does an actual call, but always just jumps to where it wants to go.
In other words, the back-translated code never uses call to protect its own stack frame from the code that it passes control to.
This means that the back-translated code is quite insecure, but we don't need it to be: it just needs to be behaviorally equivalent to the target language code that it represents.

% Finally, rather than invoking call, \dominique{7-9-2017: err, what's the reason we don't follow the same pattern for call?}.
% \lau{07-09-2017: One would use $\scall{o}{}{}$ with a pair of sealed capabilities to securely jump to this pair - that is to have this pair executed in a new stack frame. The return would happen just by using $\sxjmp{}{}$ with the $\retptrd$ and $\retptrc$. However, this would work with the local capabilities as the real implementation of $\retptrd$ would be a sealed version of the entire stack pointer. In other words, upon jumping back no extra work would have to be done. Now, however, the old stack pointer should be spliced (using the new $\ssplice{}{}$ instruction) with the stack pointer we sent away in order to regain the old stack pointer. In other words, we need something to recognise when a return happens.}
% \lau{07-09-2017: On second thought, when compiled all the code necessary for the call will be generated based on the $\scall{o}{}{}$ instruction. The real implementation of the $\retptrc$ will simply point to a piece of clean up code that splices together the old/private stack pointer with the one we got from the untrusted party. This may, however, give some issues when we want to reason about it because there will be a disconnect between where the clean up job is done in the operational semantics of the source language (namely as part of the $\sxjmp{}{}$), but in a translated program, the code that does the clean up origins with the $\scall{o}{}{}$ instruction. }

@@

Another novelty in this work is the fact that we do not want to prove general full abstraction (i.e. two source programs are behaviorally equivalent if and only if they are compiled to behaviorally equivalent target programs).
The reason is that we only want to prove a result about programs that respect the calling convention, i.e.\ that do not do anything stupid.
For example, in the old setup with global/local capabilities, when trusted code performs an \scall{o}{}{}, it should make sure that it does not store a copy of its stack pointer in a place that is accessible to the callee (e.g.\ in a register or in the callee's part of the stack).
Such sanity conditions are necessary (we cannot guarantee anything for code that does such stupid things) but we do not want to spend computation time on checking them.
Instead, we expect a reasonable compiler to guarantee in some way that its generated code never does such stupid things and then our guarantees should apply.
